---
title: "Results"
output: word_document
# output: rmarkdown::html_vignette
# vignette: >
#   %\VignetteIndexEntry{run_simulation}
#   %\VignetteEngine{knitr::rmarkdown}
#   %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  echo = FALSE,
  comment = "#>"
)
# library(vax.eff)
devtools::load_all()
library(tidyverse)
library(magrittr)
library(pander)
library(xtable)
library(purrr)
library(ggplot2)
library(tibble)
library(latex2exp)
library(janitor)
library(scales)

panderOptions('table.split.table', Inf)
panderOptions("keep.trailing.zeros", TRUE)
```

## Figure 1

```{r}
R = 0.2
pV = .75

```

Relationship of bias factor $K = R^*/R$, linkage probability $P_L$, and vaccination reporting probability $r_V$,
given $P(V) = `r pV`$, $R = `r R`$, and $N^* = N$.

```{r, fig.width=6, fig.height=4}

fig_1 = fig1(
  pV = pV,
  R = R,
  f = 0,
  lwd = .5,
  n_points = 251,
  label_x = 1.065,
  margin_offset = .05,
  add_title = FALSE)

if(FALSE)
{
  pdf(width = 7, height = 6, "figs/fig1.pdf")
  print(fig_1)
  dev.off()
}
print(fig_1)
```


## Table 1

```{r, include = FALSE}

pV = .75
rD = .9
rV = .9
N = 11 * 10^6
`N*` = N

all_results = gen_tab1(`p(V)` = pV, `p(E*|E)` = rD, `p(V*|V)` = rV, 
                       `N*` = `N*`,
                       `R` = c(1, .2),
                       `p(L|V*,E*)` = c(.95, .9, .7))

```

Simulation results with $P(V) = `r pV`$, $r_D = `r rD`$, $r_V = `r rV`$, and $N^* = N = 11 * 10^6$:

```{r, results = 'asis'}

pander::pander(all_results)

```


## Table 2

```{r, include = FALSE}

pV = .75
rD = .7
rV = .9
N = 11 * 10^6
`N*` = N

all_results = gen_tab1(`p(V)` = pV, `p(E*|E)` = rD, `p(V*|V)` = rV, 
                       `N*` = `N*`,
                       `R` = c(1, .2),
                       `p(L|V*,E*)` = c(.95, .9, .7))
```

Simulation results with $P(V) = `r pV`$, $r_D = `r rD`$, $r_V = `r rV`$, and $N^* = N = 11 * 10^6$:

```{r, results = 'asis'}
pander::pander(all_results)
```


## Table 3

```{r, include = FALSE}

pV = .75
rD = .9
rV = .9
R = .2
pL = .9
N = 11 * 10^6
multiplier = c(1.2, 1.1, 1.05, 1, .95, .9, .8)
`N*` = N * multiplier

all_results = gen_tab1(`p(V)` = pV, 
                       `p(E*|E)` = rD, 
                       `p(V*|V)` = rV, 
                       `N*` = `N*`,
                       `R` = R,
                       `p(L|V*,E*)` = pL) %>%
  rename(`$N^*$` = `$N*$`) %>%
  mutate(`$N^*$` = scales::number(`$N^*$`, big.mark = ","))

all_results = bind_cols(
  "$N^*/N$" = multiplier,
  all_results
)

```

Simulation results for varying $N^*$ (with $P(V) = `r pV`$, $r_D = `r rD`$, $r_V = `r rV`$, $p_L = `r pL`$, and $R = `r R`$):

```{r, results = 'asis'}
pander(all_results)
```

## Table 4

```{r, include = FALSE}

pV = .75
rD = .9
rV = .9
R = 1
pL = .9
N = 11 * 10^6
multiplier = c(1.2, 1.1, 1.05, 1, .95, .9, .8)
`N*` = N * multiplier

all_results = gen_tab1(`p(V)` = pV, 
                       `p(E*|E)` = rD, 
                       `p(V*|V)` = rV, 
                       `N*` = `N*`,
                       `R` = R,
                       `p(L|V*,E*)` = pL) %>%
  rename(`$N^*$` = `$N*$`) %>%
  mutate(`$N^*$` = scales::number(`$N^*$`, big.mark = ","))

all_results = bind_cols(
  "$N^*/N$" = multiplier,
  all_results
)

```

Simulation results for varying $N^*$ (with $P(V) = `r pV`$, $r_D = `r rD`$, $r_V = `r rV`$, $p_L = `r pL`$, and $R = `r R`$):

```{r, results = 'asis'}
pander(all_results)
```
